---
title: "Linear Regression Package in R"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Linear Regression Package in R}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(LabFour)
```


## Linear Regression Introduction

Linear regression is a method for creating a statistical model that can be used to predict the
future outcome based on available data. The dependent variable **y** and independent variable **X** (also called predictor) follow below simple linear regression equation:
  
  **y** = *B*~eta0~ + *B*~eta1~ * **X**
  
  *B*~eta0~ and *B*~eta1~ are the regression coefficients which can be defined as intercept and slope of the linear model, respectively. Non-zero coefficients demonstrate strong relation between the predictor (**X**) and the outcome (**y**). In addition to the simple linear regression, we can define the multiple linear regression equation as follows:
  
  **y** = *B*~eta0~ + *B*~eta1~ * **X~1~** + *B*~eta2~ * **X~2~** + ... + *B*~etan~ * **X~n~**
  
  Below plot shows an example of the simple linear equation:
  
```{r}
X <- c(0:20)
Y1 <- 7 + 0.75 * X
Y2 <- 0.5 + 2 * X
plot(X, Y1, type="l", col="blue", main="Simple Linear Model", xlab="X", ylab="Y", lwd=4, xlim=c(0,20), ylim=c(0,40))
lines(X, Y2, col="red", lwd=4)
legend(100,0.6,
       c("Y1","Y2"),lty=c(1,1),
       lwd=c(1,1),col=c("blue","red"))
```


## Methodology & Formula

This R package contains a function called **linreg()** which accepts two arguments **formula** and **data**. The function is written in RC class and the *ordinary least square* method (OSL) is used to calculate the parameters of the linear regression model.Below, one can find the detail of formula.

**Regression coefficients:**
  
  $\beta = (X^{T}X)^{-1}X^{T}y$
  
  
  **The fitted values:**
  
  $y{'} = X\beta$

**The residuals:**

$e{'} = y - y{'} = y - X\beta$

**The degrees of freedom:**

$df = n - p$

**The residual variance:**

$\sigma{'}^{2} = \frac{(e^{T}e)}{df}$
  
  **The variance of the regression coefficients:**
  
  $Var{'}(\beta) = \sigma{'}^{2}(X^{T}X)^{-1}$
  
  **The t-values for each coefficient:**
  
  $t~\beta~ = \frac{\beta}{\sqrt{Var(\beta)}}$
  
  
  ## Function Structure & Parameters
  
  In this section, function structure as well as parameters will be explained by showing examples. First of all, the predictor (independent) variable **X** will be defined by using *model.matrix()* function and then *all.vars()* function will be used for having the dependent variable, **y**. Iris data set is used in this package. Some characteristics of this data are shown below.

```{r}
data(iris)
head(iris, 4)
summary(iris)
```

Now, an object will be created and we will go through the function and explain the parameters step by step.

```{r}
mod_object <- linreg$new(formula = Petal.Length~Species, data = iris)
```

As mentioned before, the first step is to create **X** variable using *model.matrix()* function: 
  
```{r}
head(mod_object$X)
dim(mod_object$X)
```

Then we can have variable **y**:
  
```{r}
head(mod_object$Y)
dim(mod_object$Y)
```

By having **X** and **y** variables, now all linear calculations can be done via above mentioned formula.

**Regression coefficients:**
```{r}
mod_object$B
```

**The fitted values:**
```{r}
head(mod_object$Yfit)
dim(mod_object$Yfit)
```

**The residuals:**
```{r}
head(mod_object$E)
dim(mod_object$E)
```

**The degrees of freedom:**
```{r}
mod_object$P
mod_object$N
mod_object$dof
```

**The residual variance:**
```{r}
mod_object$Estd
```

**The variance of the regression coefficients:**
```{r}
mod_object$var_B
```

**The t-values for each coefficient:**
```{r}
mod_object$tval
```


The function contains several methods which return different results. We will now describe each method and show its output with an example.

**print()**\
This method prints the coefficients and their name, similar to the output of the lm function.

```{r}
mod_object$print()
```

**plot()**\
The plot method will generate below two plots using *ggplot2*.

```{r}
mod_object$plot()
```

**resid()**\
This method can be used for returning the vector of residuals e.

```{r}
head(mod_object$resid())
length(mod_object$resid())
```

**pred()**\
The pred method returns the predicted values of y.

```{r}
head(mod_object$pred())
dim(mod_object$pred())
```

**coef()**\
The coef method return the coefficients as a named vector.

```{r}
mod_object$coef()
```

**summary()**\
The summary method returns a similar printout as printed for lm objects. However, only the coefficients with their standard error, t-value and p-value as well as the estimate of $\sigma{'}$ and the degrees of freedom in the model will be presented.

```{r}
mod_object$summary()
```