---
title: "Linear Regression Package in R"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Linear Regression Package in R}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Linear Regression Introduction

Linear regression is a method for creating a statistical model that can be used to predict the
future outcome based on available data. The dependent variable **y** and independent variable **X** (also called predictor) follow below simple linear regression equation:
  
  **y** = *B*~eta0~ + *B*~eta1~ * **X**
  
  *B*~eta0~ and *B*~eta1~ are the regression coefficients which can be defined as intercept and slope of the linear model, respectively. Non-zero coefficients demonstrate strong relation between the predictor (**X**) and the outcome (**y**). In addition to the simple linear regression, we can define the multiple linear regression equation as follows:
  
  **y** = *B*~eta0~ + *B*~eta1~ * **X~1~** + *B*~eta2~ * **X~2~** + ... + *B*~etan~ * **X~n~**
  
  Below plot shows an example of the simple linear equation:
  
  ```{r}
# X <- c(1:20)
# Y1 <- 2 + 0.25 * X
# Y2 <- 2 * X
# plot(X, Y1, type="l", col="blue", main="Simple Linear Model", xlab="X", ylab="Y", lwd=4, xlim=c(0,20), ylim=c(0,40))
# lines(X, Y2, col="red", lwd=4, xlim=c(0,20), ylim=c(0,40))
# legend(100,0.6, 
#        c("Y1","Y2"),lty=c(1,1), 
#        lwd=c(1,1),col=c("blue","red"))
```


## Methodology & Formula

This R package contains a function called **linreg()** which accepts two arguments **formula** and **data**. The function is written in RC class and the *ordinary least square* method (OSL) is used to calculate the parameters of the linear regression model. Below, one can find the detail of formula.

**Regression coefficients:**
  
  $\beta = (X^{T}X)^{-1}X^{T}y$
  
  
  **The fitted values:**
  
  $y{'} = X\beta$

**The residuals:**

$e{'} = y - y{'} = y - X\beta$

**The degrees of freedom:**

$df = n - p$

**The residual variance:**

$\sigma{'}^{2} = \frac{(e^{T}e)}{df}$
  
  **The variance of the regression coefficients:**
  
  $Var{'}(\beta) = \sigma{'}^{2}(X^{T}X)^{-1}$
  
  **The t-values for each coefficient:**
  
  $t~\beta~ = \frac{\beta}{\sqrt{Var(\beta)}}$
  

```{r setup}
library(LabFour)
```
